\documentclass[11pt, a4paper]{article}

\usepackage[margin=0.75in, left=0.75in, right=0.75in, top=0.6in, bottom=0.6in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{times}

\setlist[itemize]{itemsep=0pt, topsep=2pt, partopsep=0pt, parsep=0pt, leftmargin=1.5em}
\setlist[enumerate]{itemsep=0pt, topsep=2pt, partopsep=0pt, parsep=0pt}

\begin{document}

\pagestyle{empty}

% Name
\textbf{\LARGE Srishti Rawat}\\[6pt]

% Contact Information
9084321127 \textbullet\ \hrefmailto{rawat.srishti1010@gmail.com}{rawat.srishti1010@gmail.com} \textbullet\ \href{https://linkedin.com/in/srishtirwt}{linkedin.com/in/srishtirwt} \textbullet\ \href{https://github.com/SrishtiDev}{github.com/SrishtiDev}

\hrule height0.5pt\vskip4pt

% Summary
\section*{Summary}
Full-stack software engineer (B.Tech CS, CGPA: 8.05) building AI-native applications with TypeScript, Java, and Node.js. Shipped multi-model LLM pipelines, Dockerized backends, and production REST APIs. Open source contributor to Vercel AI SDK (24k+ stars) and Mastra AI Agent Framework. Strong DSA foundation in Java; product engineer mindset focused on customer impact over code shipped.

% Technical Skills
\section*{Technical Skills}
\begin{itemize}
\item \textbf{Languages:} Java, JavaScript, TypeScript, SQL, HTML5, CSS3
\item \textbf{Frameworks \& Libraries:} Spring Boot, React, Next.js, Express.js, Tailwind CSS, Framer Motion
\item \textbf{Databases:} MySQL, MongoDB
\item \textbf{AI \& Agentic:} NVIDIA NIM, Vercel AI SDK, LangChain.js, RAG (ChromaDB), OpenAI-compatible APIs, Prompt Engineering, Agentic Coding (Claude Code, Cursor)
\item \textbf{Tools \& Platforms:} Git, GitHub, Docker, Vercel, Postman, IntelliJ IDEA, VS Code
\item \textbf{Concepts:} DSA in Java, REST API Design, OOP, MVC Architecture, System Design
\end{itemize}

% Experience
\section*{Experience}

\subsection*{HireOrbit | Next.js 14, Node.js, Express.js, Docker, NVIDIA NIM \textbar\ May 2026}
\begin{itemize}
\item Architected a 3-model AI pipeline chaining Llama 3.1-8B (extraction), Llama Nemotron-49B (ATS scoring), and MiniMax M2.7 (LaTeX generation) via NVIDIA NIM to simulate enterprise ATS systems like Workday.
\item Enforced strict JSON schema outputs from LLMs for deterministic resume parsing and keyword gap detection; implemented resilient error handling to sanitize unpredictable model outputs.
\item Containerized the Tectonic LaTeX compiler in Docker, spawning async OS-level child processes on Node.js to compile AI-generated resumes into downloadable, ATS-optimized PDFs at request time.
\end{itemize}

\subsection*{DEA - Discovery \& Execution Assistant | Next.js 15, React 19, Tailwind CSS v4, NVIDIA NIM, Minimax, Cheerio \textbar\ May 2026}
\begin{itemize}
\item Engineered a full-stack AI discovery engine delivering tailored project ideas and architectural breakdowns via NVIDIA NIM and Minimax reasoning models from user-provided tech stacks.
\item Built a server-side scraping pipeline using Cheerio to aggregate real-time GitHub trending data as live signals for AI recommendations; enforced all LLM calls server-side with zero client-side credential exposure.
\end{itemize}

\subsection*{Hospital Management System | Java, Spring Boot, REST API, MySQL \textbar\ Nov 2025}
\begin{itemize}
\item Built Spring Boot REST APIs for patient registration, doctor scheduling, and appointment workflows with a normalized MySQL schema; applied strict Controller-Service-Repository separation with transactional service boundaries.
\end{itemize}

% Open Source Contributions
\section*{Open Source Contributions}

\subsection*{Vercel AI SDK | github.com/vercel/ai \textbar\ 24k+ stars \textbar\ June 2026}
\begin{itemize}
\item Fixed a streaming bug in @ai-sdk/openai-compatible where txt-0 was hardcoded for all text segments; introduced an incrementing textPartIndex with proper text-end closure at tool call boundaries. (Issue \#15789)
\end{itemize}

\subsection*{Mastra AI Agent Framework | github.com/mastra-ai/mastra \textbar\ 6k+ stars \textbar\ June 2026}
\begin{itemize}
\item Implemented a date range picker on the /evaluation page of Mastra Studio, bringing it to parity with /metrics and /observability for time-filtered AI agent evaluation data querying.
\end{itemize}

% Education
\section*{Education}

\subsection*{ABES Engineering College, Ghaziabad, UP}
B.Tech in Computer Science (AKTU) \textbar\ CGPA: 8.05 \textbar\ Oct 2023 -- July 2027

\subsection*{Jawahar Navodaya Vidyalaya, Nainital}
Class 12th (CBSE) -- 88.6\% \textbar\ Class 10th (CBSE) -- 93.6\% \textbar\ 2022 / 2020

% Achievements
\section*{Achievements}

\subsection*{Smart India Hackathon (SIH) 2025 -- Top 50 Finalist \textbar\ 2025}
\begin{itemize}
\item Selected among Top 50 teams out of 300+ across two elimination rounds at ABES Engineering College; led Team BeHuman to build an AI-driven Train Scheduling solution for Kochi Metro Rail Limited (KMRL).
\end{itemize}

% Certifications
\section*{Certifications}

\begin{itemize}
\item Full Stack Web Development (MERN) -- Apna College, Nov 2024
\item Programming using Java -- Infosys SpringBoard, May 2025
\end{itemize}

% Extracurricular
\section*{Extracurricular}

\subsection*{Core Team Member, ABES ACM Student Chapter \textbar\ May 2024 -- May 2026}
\begin{itemize}
\item Planned and executed coding workshops, hackathons, and tech talks for 200+ participants; managed end-to-end event logistics as part of a 10-member cross-functional core team.
\end{itemize}

\end{document}